%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Karan "Damon" Kukreja 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Karan "Damon" Kukreja} % Your name
\address{2650 Haste Street Wada Hall, Room 402A Berkeley, CA 94720} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{562-231-8577 \\ 7karankukreja@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, Berkeley} \hfill {\em January 2019 - Present} 
\\ B.A. Computer Science
\\ College of Letters and Science\\
\\{\bf Cypress College} \hfill {\em August 2014 - May 2018} 
\\ AA-T Psychology\hfill



\end{rSection}

\begin{rSection}{Carrier Objective}
 To work for a tech company which allows me the opportunity to demonstrate my skills and abilities that help the company and myself to simultaneously grow.
\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Website for Tehillim School of Worship}
\\Redesigned the entire website, as well as implemented current information, roster, and schedule for the Christian Tehillim School of Worship, located in Pakistan.\\
\\{\bf Website for Artesia City Church}\\
Redesigned the entire website for the Protestant Christian ministry held at Artesia City Church.\\



\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Web Development \ & HTML, CSS, Javascript \\
Programming & Python\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{BTZ LLC.}{March 2013 - Present}{Assistant Manager}{}
\item Prepare and validate accuracy of inventory reports to ensure employees are well-stocked.
\item Review and submit invoices for vendor payment.
\item Establish and manage customer and employee relations.
\item Train new employees how to function effectively within the business and how to manage varying customer numbers.
\item Developed online presences using services such as Yelp and Google to reach potential customers. Created loyalty card programs to promote customer retention.
\end{rSubsection}

\begin{rSubsection}{Artesia City Idndian/Pakistani Church}{September 2015 - Present}{Volunteer}{}
\item Planned and hosted community events alongside church leadership in order to attract new church members.
\item Attended cultural and religious festivals to help communities connect with their faiths.
\item Lead Church’s youth group program
\end{rSubsection}

\begin{rSubsection}{Artesia City Community Development Center}{January 2012 - August 2013}{Intern}{}
\item Worked alongside the directors to manage a non-profit organization.
\item Ways we helped the community included assisting the disadvantaged with job placement and reducing youth crime rate.
\item Contacted banks and investors as well as community businesses and proposed ways that the community center would benefit everyone.
\item Marketing and community outreach
\item Active volunteering within the center’s hosted events, such as the Homeless count, in which the organization split into groups of five and distributed food to the homeless that resided under riverbeds. The homeless population was then brought to awareness about our organization, and how we can assist them in solving their problems.
\end{rSubsection}



\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} 
Dean's List (Cypress College) - Placed on the Dean's List at Cypress College from August of 2014 to June of 2018.
\item President's List (Cypress College) Placed on the President's list at Cypress College from August of 2014 to June of 2018.
\item Graduated from Cypress College in May of 2018 with highest honors. GPA: 3.99
\end{rSection}



%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item 1st Place Men's Physique Competition in Summer of 2016.
\item Sponsored Athlete for MAN Sports and Nutritox Vitamins from November 2014- Current.
\item Global representative for MAN Sports on bodybuilding.com from November 2014- Current.
\item Online Fitness Coaching/Contest Preparation for Men's Physique Competitions from June 2015 - Current

%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

\end{rSection}

\begin{rSection}{Personal Traits}
\item Highly motivated and able to disassociate from emotions when necessary, to act and think in a more logical manner.
\item Strong ability in adapting to varying circumstances.
\item Ability to work as an individual that can act as a leader and a follower, when needed.
\end{rSection}
\end{document}
